Imprecise Computing in Datapath Design: An Overclocking Approach

### 2013-05-10 TCAD2013/overclocking_tcad.tex
Add Section: Area Overhead

According to the existing literatures, one way to operating circuits beyond the deterministic region is to relax the design constraints and the guard-bands that are conventionally used to avoid the worst cases. Research in this area is based on the observations that in practice, the worst case happens rarely. A series of work known as ``Better-Than-Worst-Case (BTWC) Design'' introduced a universal framework to push the circuit performance to its limits~\cite{BetterThanWS2005}. In general, a BTWC design is composed of cores and checkers. The cores are operated with high performance by eliminating the guard-bands, meanwhile the possible timing errors are diagnosed by the checkers. Optionally the system can be recovered at the observation of errors. As an exemplary design, the Razor project~\cite{Razor2003,Razor2004} was proposed to shave the conservative timing margins by overscaling the supply voltage and clock frequency, while monitoring the output error rates by utilizing a self-checking circuit. This work demonstrated that the benefits brought by removing the safe margin outweigh the cost of monitoring and recovering from errors. For example, $22\%$ or over $30\%$ power consumption can be saved with $\sim0.01\%$ or $\sim1\%$ error rates at the output, respectively. Related work includes a similar frequency overscaling technique by operating circuits slightly slower than the critical path delay with dedicated checker circuits to ensure that timing errors will not occur~\cite{TEAtime2004}, developing timing analysis tools that decide the optimum operating frequencies in the non-deterministic region due to process variation~\cite{ProbabilisticSTA} or xxx.

@@

While the aforementioned literatures take advantage of the fact that only specific input patterns could cause timing errors, research on imprecise architectures take this one step further by designing simplified circuits for peformance/energy efficiency. For example, Lu et~al. proposed a ``shrinking'' datapath that can be utilized to mimic and speculate the original logic functions~\cite{IntelSpeeding}. Kulkarni et.al. described an underdesigned $2\times2$ multiplier unit, of which the worst case was replaced by a normal case based on the straight-forward Karnaugh Map analysis~\cite{Undersigned2x2multiplier}. In both cases, reduction of area and power consumption can be achieved with the cost of accuracy. In addition, Gupta et.al. developed approximate adders at the transistor level and compared the energy efficiency of their proposed architectures over truncation of input word-length of conventional structures~\cite{Gupta2013TransCADICS}.

However, the limitations of the existing work should not be neglected. Firstly, some techniques, such as employing several voltages regions within a ripple carry adder, are not practical to achieve in real situations, and the overhead of applying this technique is not discussed. Secondly, many studies propose alternative architectures, which means the adaptability of this kind of technique is limited on current hardware platforms. More importantly, correct results would never be obtained by using approximate architectures. Thirdly, the link between the probability of output correctness and energy savings or performance improvements are rarely analyzed from current research.

@@

%Lena image
\begin{figure*}[htbp]
  %\vspace{-2ex}
  \centering
  \subfigure[425MHz,~n=8~,~SNR=47.97dB]{
  \begin{minipage}[c]{0.24\textwidth}
    \centering
    \includegraphics[width=1.8in]{./Figures/Exp/FIR/LenaImages/FIRLena_T8.eps}
  \end{minipage}%
  }% This is important! use % to indicate same line, otherwise new line
  \subfigure[450MHz,~n=8,~SNR=44.94dB]{
  \begin{minipage}[c]{0.24\textwidth}
    \centering
    \includegraphics[width=1.8in]{./Figures/Exp/FIR/LenaImages/FIRLena_T65.eps}
  \end{minipage}
  }%
  \subfigure[480MHz,~n=8,~SNR=21.58dB]{
  \begin{minipage}[c]{0.24\textwidth}
    \centering
    \includegraphics[width=1.8in]{./Figures/Exp/FIR/LenaImages/FIRLena_T62.eps}
  \end{minipage}
  }%
  \subfigure[520MHz,~n=8,~SNR=10.03dB]{
  \begin{minipage}[c]{0.24\textwidth}
    \centering
    \includegraphics[width=1.8in]{./Figures/Exp/FIR/LenaImages/FIRLena_T6.eps}
  \end{minipage}
  }\vspace{-1ex}
  \subfigure[425MHz,~n=7,~SNR=26.02dB]{
  \begin{minipage}[c]{0.24\textwidth}
    \centering
    \includegraphics[width=1.8in]{./Figures/Exp/FIR/LenaImages/FIRLena_Q7T10.eps}
  \end{minipage}%
  }% This is important! use % to indicate same line, otherwise new line
  \subfigure[450MHz,~n=5,~SNR=21.76dB]{
  \begin{minipage}[c]{0.24\textwidth}
    \centering
    \includegraphics[width=1.8in]{./Figures/Exp/FIR/LenaImages/FIRLena_Q4T10.eps}
  \end{minipage}
  }%
  \subfigure[480MHz,~n=2,~SNR=6.57dB]{
  \begin{minipage}[c]{0.24\textwidth}
    \centering
    \includegraphics[width=1.8in]{./Figures/Exp/FIR/LenaImages/FIRLena_Q2T10.eps}
  \end{minipage}
  }%
  \subfigure[520MHz,~n=1,~SNR=3.95dB]{
  \begin{minipage}[c]{0.24\textwidth}
    \centering
    \includegraphics[width=1.8in]{./Figures/Exp/FIR/LenaImages/FIRLena_Q1T10.eps}
  \end{minipage}
  }
%\vspace{-2ex}
\caption{Output images of the FIR filter for both overclocking scenario (top row) and traditional scenario (bottom row) under various operating frequencies.}
\label{FIR_Lena}
%\vspace{-2ex}
\end{figure*}

@@

\subsection{Potential Benefits in Circuit Design}
%The results can be interpreted in two folds.
Our results could be of interest to a circuit designer in two ways. Typically, either the designer will want to create a circuit that can run at a given frequency with the minimum possible MRE, or the algorithm designer will wish to run as fast as possible whilst maintaining a specific error tolerance. In the first case, the experimental results for all five example designs on FPGA are summarized in Table~\ref{Ratio_MRE} in terms of the relative reduction of MRE as given in~(\ref{Relative Reduction MRE}) where $MRE_{Trad}$ and $MRE_{ovrc}$ denote the value obtained in the traditional scenario and in the overclocking scenario, respectively.
\begin{eqnarray}\label{Relative Reduction MRE}
%\small
\scriptsize
  \frac{MRE_{Trad}-MRE_{ovrc}}{MRE_{Trad}}\times 100\%
\end{eqnarray}
\normalsize
%\vspace{-2ex}

@@

\subsection{Area Overhead}
\begin{table*}[htbp]
 %\vspace{-2ex}
 %% increase table row spacing, adjust to taste
   \renewcommand{\arraystretch}{1.05}
   \setlength{\tabcolsep}{3.5pt}
   %\caption{Relative Reduction of MRE in Overclocking Scenario for Various Normalized Frequencies Based on~(\ref{Relative Reduction MRE}).}
   \caption{Area Overhead of Our Approach with respect to Given Frequency Requirements}
%   \vspace{-2ex}
   \centering
   \footnotesize
   %\vspace{-4mm}
   \begin{threeparttable}
   \begin{tabular}{c|cc|cc|cc|cc|cc||cc}
     \hline
     \hline
     \multirow{2}*{\begin{tabular}{c}\textbf{Normalized}\\\textbf{Frequency}\end{tabular}} &
     \multicolumn{2}{c|}{\textbf{FIR}} &
     \multicolumn{2}{c|}{\textbf{Sobel}} &
     \multicolumn{2}{c|}{\textbf{IIR}} &
     \multicolumn{2}{c|}{\textbf{Butterworth}} &
     \multicolumn{2}{c||}{\textbf{DCT4}} &
     \multicolumn{2}{c}{\textbf{Geo.Mean}}\\
     &  {LUTs} & {Slices } &  {LUTs} & {Slices } &  {LUTs} & {Slices  }
     &  {LUTs} & {Slices } &  {LUTs} & {Slices } &  {LUTs} & {Slices}\\
     \hline
     1.04 & 1.24	& 1.05  & 1.12 &	1.22 &	 1.26 &	1.42 &	 1.16 &	 1.11 &	 1.13 &	 1.00 & 1.18 & 1.15\\
     1.08 & 1.24	& 1.05	& 1.03 &	1.08 &	 1.26 &	1.42 &	 1.16 &	 1.11 &	 1.11 &	 1.15 & 1.16 & 1.16\\
     1.12 & 1.24	& 1.05   & 1.03 &	1.08 &	 1.26 & 1.42 &	 1.37 &	1.54  &	 2.30 &	 2.17 & 1.38 & 1.40\\
     1.16 & 2.95	& 2.56   & 1.03 &	1.08 &	 1.61 & 1.71 &	 1.99 &	 2.03  &	 4.60 &	 2.89 &2.14 & 1.95\\
     1.20 & 2.95	& 2.56   & 1.66 &	1.39 &	 2.77 &	3.48 &	3.17 &	 3.50  &	 N/A\tnote{*}	  & N/A\tnote{*} & 2.56 & 2.57 \\
     1.24 & 4.42	& 3.15  & 4.00 &	3.55 &	 7.87 &	6.73 &	6.92 &	 5.25  &	 N/A\tnote{*}	  & N/A\tnote{*} & 5.57 & 4.46\\
     1.28 & 4.42	& 3.15   & 4.00 &	3.55 &	 N/A\tnote{*}	    &   N/A\tnote{*}     &	6.92 &	 5.25  &	N/A\tnote{*}	  & N/A\tnote{*} & 4.97& 3.89\\
     1.32 & 4.42	& 3.15   & N/A\tnote{*}	  &	 N/A\tnote{*}	    &	 N/A\tnote{*}	    &	 N/A\tnote{*}   & N/A\tnote{*}   & N/A\tnote{*}    &    N/A\tnote{*}   & N/A\tnote{*} & 4.42	& 3.15 \\
     \hline
     \hline
   \end{tabular}
   \normalsize
   \begin{tablenotes}
   \footnotesize
    \item[*] Current frequency cannot be achieved in the traditional scenario. These points are excluded from the calculation of geometric means.
   \end{tablenotes}
   \end{threeparttable}
   \label{Ratio_MRE}
% \vspace{-1ex}
 \end{table*}

 \begin{table*}[htbp]
 %\vspace{-2ex}
 %% increase table row spacing, adjust to taste
   \renewcommand{\arraystretch}{1.05}
   \setlength{\tabcolsep}{3.5pt}
   %\caption{Frequency Speedups in Overclocking Scenario Under Various Error Budgets.}
   \caption{Area Overhead of Our Approach with respect to Given Error Budgets.}
%   \vspace{-2ex}
   \label{Exp_Real_Inputs}
   \centering
   \footnotesize
   \begin{tabular}{c|cc|cc|cc|cc|cc||cc}
     \hline
     \hline
     \multirow{2}*{\begin{tabular}{c}\textbf{Error Budget}\\\textbf{\%}\end{tabular}} &
     \multicolumn{2}{c|}{\textbf{FIR}} &
     \multicolumn{2}{c|}{\textbf{Sobel}} &
     \multicolumn{2}{c|}{\textbf{IIR}} &
     \multicolumn{2}{c|}{\textbf{Butterworth}} &
     \multicolumn{2}{c||}{\textbf{DCT4}} &
     \multicolumn{2}{c}{\textbf{Geo.Mean}} \\
     %\multirow{2}*{\begin{tabular}{c}\textbf{Geo.}\\\textbf{Mean}\end{tabular}}\\
     & {LUTs} & {Slices } &  {LUTs} & {Slices } &  {LUTs} & {Slices }
     & {LUTs} & {Slices } &  {LUTs} & {Slices } &  {LUTs} & {Slices }\\
     \hline
     0.05 & 1.00&	1.00& 1.00&	1.00& 1.00&	 1.00&	1.00&	 1.00&	1.00&	 1.00  &1.00  &  1.00\\
     0.5  & 1.02&	1.15& 1.00&	1.00& 1.00&	 1.00&	1.00&	 1.00&	1.00&	 1.00   &1.00 &1.03\\
     1    & 1.02&	1.15& 1.00&	1.00& 1.00&	 1.00&	1.00&	 1.00&	1.00&	 1.00   &1.00 &1.03\\
     5    & 1.24&	1.05& 1.00&	1.00& 1.26&   1.42&   1.65&   1.11&	 1.00&    1.00   &1.13    &1.11\\
     10   & 1.24&	1.05& 1.12&	1.22& 1.26&	1.42& 1.65&	1.11& 1.11&	 1.15&    1.18    &1.18\\
     20   & 1.24&	1.05& 1.03&	1.08& 1.26&	1.42& 6.92&	 5.25&   3.45&	 2.17   &2.07    &1.79\\
     50   & 2.95&	2.56& 4.00&	3.55& 7.87&	6.73& 6.92&	 5.25&   3.45&	 2.12	&4.67 &3.70\\
     \hline
     \hline
   \end{tabular}
   \normalsize
   \label{Max_Frequency}
%   \vspace{-3ex}
 \end{table*}

@@

%\begin{figure}[htbp]
%	\centering
%	\includegraphics[width=3.3in]{./Figures/Error_LUT45.eps}
%	\caption{LUT=45}
%\end{figure}
%
%\begin{figure}[htbp]
%	\centering
%	\includegraphics[width=3.3in]{./Figures/Error_LUT35.eps}
%	\caption{LUT=35}
%\end{figure}
%
%\begin{figure}[htbp]
%	\centering
%	\includegraphics[width=3.3in]{./Figures/Error_LUT25.eps}
%	\caption{LUT=25}
%\end{figure}
%
%\begin{figure}[htbp]
%	\centering
%	\includegraphics[width=3.3in]{./Figures/Error_LUT15.eps}
%	\caption{LUT=15}
%\end{figure}
%

>>>>

According to the existing literatures, one way to operating circuits beyond the deterministic region is to relax the design constraints and the guard-bands that are conventionally used to avoid the worst cases. Research in this area is based on the observations that in practice, the worst case happens rarely. A series of work known as ``Better-Than-Worst-Case (BTWC) Design'' introduced a universal framework to push the circuit performance to its limits~\cite{BetterThanWS2005}. In general, a BTWC design is composed of cores and checkers. The cores are operated with high performance by eliminating the guard-bands, meanwhile the possible timing errors are diagnosed by the checkers. Optionally the system can be recovered at the observation of errors. As an exemplary design, the Razor project~\cite{Razor2003,Razor2004} was proposed to shave the conservative timing margins by overscaling the supply voltage and clock frequency, while monitoring the output error rates by utilizing a self-checking circuit. This work demonstrated that the benefits brought by removing the safe margin outweigh the cost of monitoring and recovering from errors. For example, $22\%$ or over $30\%$ power consumption can be saved with $\sim0.01\%$ or $\sim1\%$ error rates at the output, respectively. Related work includes a similar frequency overscaling technique by operating circuits slightly slower than the critical path delay with dedicated checker circuits to ensure that timing errors will not occur~\cite{TEAtime2004}, or developing timing analysis tools that decide the optimum operating frequencies in the non-deterministic region due to process variation~\cite{ProbabilisticSTA}.

@@

While the aforementioned literatures take advantage of the fact that only specific input patterns could cause timing errors, research on imprecise architectures take this one step further by designing simplified circuits for peformance/energy efficiency. For example, Lu et~al. proposed a ``shrinking'' datapath that can be utilized to mimic and speculate the original logic functions~\cite{IntelSpeeding}. Kulkarni et.al. described an underdesigned $2\times2$ multiplier unit, of which the worst case was replaced by a normal case based on the straight-forward Karnaugh-Map analysis~\cite{Undersigned2x2multiplier}. In both cases, reduction of area and power consumption can be achieved with the cost of accuracy. In addition, Gupta et~al. developed approximate adders at the transistor level and compared the energy efficiency of their proposed architectures over truncation of input word-length of conventional structures~\cite{Gupta2013TransCADICS}.

However, the limitations of the existing work should not be neglected. Firstly, some techniques, such as employing several voltages regions within a ripple carry adder, are not practical to achieve in real situations, and the overhead of applying this technique is not discussed. Secondly, many studies propose alternative architectures, which means the adaptability of this kind of technique is limited on current hardware platforms. More importantly, correct results would never be obtained as long as the approximate architectures were employed. Thirdly, the link between the probability of output correctness and energy savings or performance improvements are rarely analyzed from current research.

@@

%Lena image
\begin{figure*}[htbp]
  %\vspace{-2ex}
  \centering
  \subfigure[425MHz,~n=8~,~SNR=47.97dB]{
  \begin{minipage}[c]{0.24\textwidth}
    \centering
    \includegraphics[width=1.8in]{./Figures/Exp/FIR/LenaImages/FIRLena_T8.eps}
  \end{minipage}%
  }% This is important! use % to indicate same line, otherwise new line
  \subfigure[450MHz,~n=8,~SNR=44.94dB]{
  \begin{minipage}[c]{0.24\textwidth}
    \centering
    \includegraphics[width=1.8in]{./Figures/Exp/FIR/LenaImages/FIRLena_T65.eps}
  \end{minipage}
  }%
  \subfigure[480MHz,~n=8,~SNR=21.58dB]{
  \begin{minipage}[c]{0.24\textwidth}
    \centering
    \includegraphics[width=1.8in]{./Figures/Exp/FIR/LenaImages/FIRLena_T62.eps}
  \end{minipage}
  }%
  \subfigure[520MHz,~n=8,~SNR=10.03dB]{
  \begin{minipage}[c]{0.24\textwidth}
    \centering
    \includegraphics[width=1.8in]{./Figures/Exp/FIR/LenaImages/FIRLena_T6.eps}
  \end{minipage}
  }
  \subfigure[425MHz,~n=7,~SNR=26.02dB]{
  \begin{minipage}[c]{0.24\textwidth}
    \centering
    \includegraphics[width=1.8in]{./Figures/Exp/FIR/LenaImages/FIRLena_Q7T10.eps}
  \end{minipage}%
  }% This is important! use % to indicate same line, otherwise new line
  \subfigure[450MHz,~n=5,~SNR=21.76dB]{
  \begin{minipage}[c]{0.24\textwidth}
    \centering
    \includegraphics[width=1.8in]{./Figures/Exp/FIR/LenaImages/FIRLena_Q4T10.eps}
  \end{minipage}
  }%
  \subfigure[480MHz,~n=2,~SNR=6.57dB]{
  \begin{minipage}[c]{0.24\textwidth}
    \centering
    \includegraphics[width=1.8in]{./Figures/Exp/FIR/LenaImages/FIRLena_Q2T10.eps}
  \end{minipage}
  }%
  \subfigure[520MHz,~n=1,~SNR=3.95dB]{
  \begin{minipage}[c]{0.24\textwidth}
    \centering
    \includegraphics[width=1.8in]{./Figures/Exp/FIR/LenaImages/FIRLena_Q1T10.eps}
  \end{minipage}
  }
%\vspace{-2ex}
\caption{Output images of the FIR filter for both overclocking scenario (top row) and traditional scenario (bottom row) under various operating frequencies.}
\label{FIR_Lena}
%\vspace{-2ex}
\end{figure*}

@@

\subsection{Potential Benefits in Circuit Design}
%The results can be interpreted in two folds.
As we mentioned in Section~xxx, our results could be of interest to a circuit designer in two ways. Typically, either the designer will want to create a circuit that can run at a given frequency with the minimum possible MRE, or the algorithm designer will wish to run as fast as possible whilst maintaining a specific error tolerance. For the first design target, the experimental results for all five example designs on FPGA are summarized in Table~\ref{Ratio_MRE} in terms of the relative reduction of MRE as given in~(\ref{Relative Reduction MRE}) where $MRE_{Trad}$ and $MRE_{ovrc}$ denote the value obtained in the traditional scenario and in the overclocking scenario, respectively.

\begin{eqnarray}\label{Relative Reduction MRE}
  \frac{MRE_{Trad}-MRE_{ovrc}}{MRE_{Trad}}\times 100\%
\end{eqnarray}

@@

\subsection{Area Overhead}
For both aforementioned design goals, it should be noted that an extra benefit of using the traditional approach is that reducing datapath precision would potentially leads to a smaller design, in comparison to our proposed overclocking scenario. Consequently, the area overheads of our approach are summarized in Table xxx and Table xxx for both design goals. In our experiments, the area overhead is evaluated in terms of the number of LUTs and Slices in the FPGA technology, while similar metrics can also be employed if applying our approach into other hardware platforms. It can be seen that for a given frequency requirement with minimum possible errors, the geometric mean of area overhead ranges from $1.16\times$ and $1.15\times$ to $5.57\times$ and $4.46\times$ for LUTs and Slices, respectively.

An even smaller area overhead can be found for a specified error budget with the maximum clock frequencies. As seen in Table xxx, the geometric mean of area overhead in terms of LUTs and Slices is $1.00\times\sim4.67\times$ and $1.00\times\sim3.70\times$ respectively. Notice that an area overhead of $1\times$ means both the overclocking scenario and the traditional scenario use the original precision, however the former achieves frequency speedups as seen in Tablexxx, because a specific error budget can be tolerated.

In general, we can observe a relatively small area overhead of our approach, especially when frequency is initially increased or with a small error budget (i.e. $\sim10\%$).

\begin{table*}[htbp]
 %% increase table row spacing, adjust to taste
   \renewcommand{\arraystretch}{1.05}
   \setlength{\tabcolsep}{3.5pt}
   \caption{Area Overhead of Our Approach with respect to Given Frequency Requirements}
   \centering
   \footnotesize
   \begin{threeparttable}
   \begin{tabular}{c|cc|cc|cc|cc|cc||cc}
     \hline
     \hline
     \multirow{2}*{\begin{tabular}{c}\textbf{Normalized}\\\textbf{Frequency}\end{tabular}} &
     \multicolumn{2}{c|}{\textbf{FIR}} &
     \multicolumn{2}{c|}{\textbf{Sobel}} &
     \multicolumn{2}{c|}{\textbf{IIR}} &
     \multicolumn{2}{c|}{\textbf{Butterworth}} &
     \multicolumn{2}{c||}{\textbf{DCT4}} &
     \multicolumn{2}{c}{\textbf{Geo.Mean}}\\
     &  {LUTs} & {Slices } &  {LUTs} & {Slices } &  {LUTs} & {Slices  }
     &  {LUTs} & {Slices } &  {LUTs} & {Slices } &  {LUTs} & {Slices}\\
     \hline
     1.04 & 1.24	& 1.05  & 1.12 &	1.22 &	 1.26 &	1.42 &	 1.16 &	 1.11 &	 1.13 &	 1.00 & 1.18 & 1.15\\
     1.08 & 1.24	& 1.05	& 1.03 &	1.08 &	 1.26 &	1.42 &	 1.16 &	 1.11 &	 1.11 &	 1.15 & 1.16 & 1.16\\
     1.12 & 1.24	& 1.05   & 1.03 &	1.08 &	 1.26 & 1.42 &	 1.37 &	1.54  &	 2.30 &	 2.17 & 1.38 & 1.40\\
     1.16 & 2.95	& 2.56   & 1.03 &	1.08 &	 1.61 & 1.71 &	 1.99 &	 2.03  &	 4.60 &	 2.89 &2.14 & 1.95\\
     1.20 & 2.95	& 2.56   & 1.66 &	1.39 &	 2.77 &	3.48 &	3.17 &	 3.50  &	 N/A\tnote{*}	  & N/A\tnote{*} & 2.56 & 2.57 \\
     1.24 & 4.42	& 3.15  & 4.00 &	3.55 &	 7.87 &	6.73 &	6.92 &	 5.25  &	 N/A\tnote{*}	  & N/A\tnote{*} & 5.57 & 4.46\\
     1.28 & 4.42	& 3.15   & 4.00 &	3.55 &	 N/A\tnote{*}	    &   N/A\tnote{*}     &	6.92 &	 5.25  &	N/A\tnote{*}	  & N/A\tnote{*} & 4.97& 3.89\\
     1.32 & 4.42	& 3.15   & N/A\tnote{*}	  &	 N/A\tnote{*}	    &	 N/A\tnote{*}	    &	 N/A\tnote{*}   & N/A\tnote{*}   & N/A\tnote{*}    &    N/A\tnote{*}   & N/A\tnote{*} & 4.42	& 3.15 \\
     \hline
     \hline
   \end{tabular}
   \normalsize
   \begin{tablenotes}
   \footnotesize
    \item[*] Current frequency cannot be achieved in the traditional scenario. These points are excluded from the calculation of geometric means.
   \end{tablenotes}
   \end{threeparttable}
   \label{Ratio_MRE}
 \end{table*}

 \begin{table*}[htbp]
 %% increase table row spacing, adjust to taste
   \renewcommand{\arraystretch}{1.05}
   \setlength{\tabcolsep}{3.5pt}
   \caption{Area Overhead of Our Approach with respect to Given Error Budgets.}
   \label{Exp_Real_Inputs}
   \centering
   \footnotesize
   \begin{tabular}{c|cc|cc|cc|cc|cc||cc}
     \hline
     \hline
     \multirow{2}*{\begin{tabular}{c}\textbf{Error Budget}\\\textbf{\%}\end{tabular}} &
     \multicolumn{2}{c|}{\textbf{FIR}} &
     \multicolumn{2}{c|}{\textbf{Sobel}} &
     \multicolumn{2}{c|}{\textbf{IIR}} &
     \multicolumn{2}{c|}{\textbf{Butterworth}} &
     \multicolumn{2}{c||}{\textbf{DCT4}} &
     \multicolumn{2}{c}{\textbf{Geo.Mean}} \\
     %\multirow{2}*{\begin{tabular}{c}\textbf{Geo.}\\\textbf{Mean}\end{tabular}}\\
     & {LUTs} & {Slices } &  {LUTs} & {Slices } &  {LUTs} & {Slices }
     & {LUTs} & {Slices } &  {LUTs} & {Slices } &  {LUTs} & {Slices }\\
     \hline
     0.05 & 1.00&	1.00& 1.00&	1.00& 1.00&	 1.00&	1.00&	 1.00&	1.00&	 1.00  &1.00  &  1.00\\
     0.5  & 1.02&	1.15& 1.00&	1.00& 1.00&	 1.00&	1.00&	 1.00&	1.00&	 1.00   &1.00 &1.03\\
     1    & 1.02&	1.15& 1.00&	1.00& 1.00&	 1.00&	1.00&	 1.00&	1.00&	 1.00   &1.00 &1.03\\
     5    & 1.24&	1.05& 1.00&	1.00& 1.26&   1.42&   1.65&   1.11&	 1.00&    1.00   &1.13    &1.11\\
     10   & 1.24&	1.05& 1.12&	1.22& 1.26&	1.42& 1.65&	1.11& 1.11&	 1.15&    1.18    &1.18\\
     20   & 1.24&	1.05& 1.03&	1.08& 1.26&	1.42& 6.92&	 5.25&   3.45&	 2.17   &2.07    &1.79\\
     50   & 2.95&	2.56& 4.00&	3.55& 7.87&	6.73& 6.92&	 5.25&   3.45&	 2.12	&4.67 &3.70\\
     \hline
     \hline
   \end{tabular}
   \normalsize
   \label{Max_Frequency}
 \end{table*}

@@
